Formalization of Typed Lua

### 2015-06-05 doc/papers/paper/paper.tex

\title{Optional typing for Lua}

@@

\begin{abstract}
This is the text of the abstract.
\end{abstract}

>>>>

\title{Formalization of Typed Lua}

@@

\begin{abstract}
Dynamically typed languages such as Lua avoid static types in order
to have a simpler and more flexible language, because their programmers
to not need to bother with abstracting types that need to be validated
by a type checker. In contrast, statically typed languages provide
earlier detection of many defects, and a better framework for structuring
large programs. The advantages of static types often lead programmers to
migrate from a dynamically typed to a statically typed language when
their simple scripts evolve into complex programs.

Optional type systems are one way to have both static and dynamic
typing in the same language while keeping its original semantics,
making evolving a program from dynamic to static typing a matter of
describing the implied types that it it using and adding annotations
to make those types explicit. Designing an optional type system for
an existing dynamically typed language is challenging, as its types
should feel natural to programmers that are already familiar with
this language.

In this work, we give a formal description of Typed Lua, an
optional type system for Lua, with a focus on its novel type system
features: incremental evolution of record and object types via
imperative update that does not sacrifice width subtyping,
and combining flow typing with multiple assignment and with functions that
return multiple values. While our type system is tailored to the
features and idioms of Lua, its features can be adapted to other
imperative scripting languages.
\end{abstract}
